More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-11-16 2016-Weak-FH-Bisim/WeakBisim.tex

\subsection{Composition properties}
\TODO{Ludo: in the next 2 theorems I have a doubt about the biguplus of post p : not sure they should be disjoint, but else we need to do a complex composition  of posts}
\begin{lemma}[Weak OT decomposition]\label{lem-decompose} 
	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction. Suppose $\gamma_{j_0}=[\beta_0..\beta_n]$
		 then there exist $\Pred\,'$,  
		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{and~~}  \bigcup_{\begin{array}{l}
p\in[0..n]
\end{array}} J_{p} = J\cap\Holes(Q) \qquad
 \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
 \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
		\land \!\!\bigwedge_{p=0}^n(\alpha_p= \beta_p\land \Pred_p) \qquad\text{and~}
\Post=\Post\,'\uplus\!\! \biguplus_{p=0}^n
		\Post_p  
		\end{mathpar}
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}
\LUDO{A V2 by Ludo} \TODO{We will check notation  $\alpha_p=...$}

\begin{proof}
By lemma \ref{lem-rel-OT-WOT} we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}} 
\end{mathpar}
implies 	\\			
$			
	P[Q]_{j_0}	\models		
\Big(\forall i \in [0\ldots n].\openrule
    {
       \set{\gamma^1_i},\Pred^1_i,\Post^1_i   }
         {\ostate{s^1_i} \OTarrow {\tau} \ostate{s^1_{i+1}}}\, \wedge\,
\openrule
         {
           \set{\gamma^2},\Pred\,^2,\Post^2 }
         {\ostate{s^2} \OTarrow {\alpha} \ostate{s'^2}}
\,\wedge\,
\forall i \in [0\ldots m].\openrule
         {
           \set{\gamma^3_i},\Pred\,^3_i, \Post^3   }
         {\ostate{s^3_i} \OTarrow {\tau} \ostate{s^3_{i+1}}}
\Big) 
$

such that...\\

On other hand by Theorem \ref{thm-composability} we have:

\TODO{La preuve page 27 est difficile a suivre...}

>>>>

\subsection{Composition properties}
\TODO{Ludo: in the next 2 theorems I have a doubt about the biguplus of post p : not sure they should be disjoint, but else we need to do a complex composition  of posts}
\begin{lemma}[Weak OT decomposition]\label{lem-decompose} 
	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction. Suppose $\gamma_{j_0}=[\beta_0..\beta_n]$
		 then there exist $\Pred\,'$,  
		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{and~~}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad
 \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
 \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
		\land \!\!\bigwedge_{p=0}^n(\alpha_p= \beta_p\land \Pred_p) \qquad\text{and~}
\Post=\Post\,'\uplus\!\! \biguplus_{p=0}^n
		\Post_p  
		\end{mathpar}
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}
\LUDO{A V2 by Ludo}
\newpage
\begin{proof} Suppose we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall i \in [0\ldots n]	\,		
	P[Q]_{j_0}	\models		
\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {\ostate{s^1_i} \OTarrow {\tau} \ostate{s^1_{i+1}}}$
~and~ $\forall i \in [0\ldots m] \, P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^3_i},\Pred\,^3_i, \Post_i^3   }
         {\ostate{s^3_i} \OTarrow {\tau} \ostate{s^3_{i+1}}}
$\\
and $ P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {\ostate{s^2} \OTarrow {\alpha} \ostate{s'^2}}
$ where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{n}\subst{\Post_i^1}\land (\bigwedge_{i=0}^m\Pred\,^3_i\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}\\
\Post=\biguplus_{i=0}^{m}(\Post^3_i\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}
$

We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$,  we have obtain of each case:
\begin{enumerate}
\item $P\models{\openrule
			{
				\beta_{ij}^{1j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred_i^1}',  
				{\Post_i^1}'}
			{\ostate{s_{il}^{1l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{s_{il}'^{\,1l\in L\setminus L_Q}}}
		}%\]
	\,\text{and~~}
		%\[
		Q\models{\openrule
			{
				\beta_{ij}^{1j\in J\cap\Holes(Q)}, {\Pred_i^1}'',  
				{\Post_i^1}''}
			{\ostate{s_{il}^{1l\in L_Q}} \OTarrow {\alpha^1_Q}
				\ostate{s_{il}'^{\,1l\in L_Q}}}
		}%\]
$and  $\Pred_i^1 \iff {\Pred_i^1}'
		\land {\Pred_i^1}''\land \alpha^1_Q=\beta^1_{ij_0}$, $\Post_i^1={\Post_i^1}'\uplus 
		{\Post_i^1}''$ where ${\Post_i^1}''$ is the restriction of $\Post_i^1$ over variables of $\Leaves(Q)$.
\item
 $P\models{\openrule
			{
				\beta_{ij}^{3j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred_i^3}',  
				{\Post_i^3}'}
			{\ostate{s_{il}^{3l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{s_{il}'^{\,3l\in L\setminus L_Q}}}
		}%\]
	\,\text{and~~}
		%\[
		Q\models{\openrule
			{
				\beta_{ij}^{3j\in J\cap\Holes(Q)}, {\Pred_i^3}'',  
				{\Post_i^3}''}
			{\ostate{s_{il}^{3l\in L_Q}} \OTarrow {\alpha^3_Q}
				\ostate{s_{il}'^{\,3l\in L_Q}}}
		}%\]
$and  $\Pred_i^3 \iff {\Pred_i^3}'
		\land {\Pred_i^3}''\land \alpha^3_Q=\beta^3_{ij_0}$, $\Post_i^3={\Post_i^3}'\uplus 
		{\Post_i^3}''$ where ${\Post_i^3}''$ is the restriction of $\Post_i^3$ over variables of $\Leaves(Q)$.

\item 
 $
		P\models{\openrule
			{
				\beta_j^{2j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^2}',  
				{\Post^2}'}
			{\ostate{s_l^{2l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{s_l'^{\,2l\in L\setminus L_Q}}}
		}%\]
	\,\text{and~~}
		%\[
		Q\models{\openrule
			{
				\beta_j^{2j\in J\cap\Holes(Q)}, {\Pred^2}'',  
				\Post\,''}
			{\ostate{s_l^{2l\in L_Q}} \OTarrow {\alpha^2_Q}
				\ostate{s_l'^{\,2l\in L_Q}}}
		}%\]
		$
		and  $\Pred^2 \iff {\Pred^2}'
		\land {\Pred^2}''\land \alpha^2_Q=\beta^2_{j_0}$, $\Post^2={\Post^2}'\uplus 
		{\Post^2}''$ where ${\Post^2}''$ is the restriction of $\Post^2$ over variables of $\Leaves(Q)$.
\end{enumerate}
By Lemma \ref{lem-rel-OT-WOT} we can conclude that we have:

\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
\end{mathpar}

Where

\TODO{j'explicite Pred', Post', ect... Mais je ne sais pas trop pour Q???}
